Baseline centering problem

### 2018-11-29 paper/tangotd.tex

In the reversible case, $\mu\Delta$ is symmetric.\footnote{$\rho \Delta$
can be symmetric if and only if $\rho=\mu$. Indeed, if $\rho \Delta$ is
symmetric then $\rho=\rho'$ and $\rho$ is the stationary distribution.} We can use the
Dirichlet form which amounts to $L\deq\mu(\mu\Delta)^{-1}\mu$; then
$L\Delta=\mu$ and we have to prove that $\mu\Phi B\transp{\Phi}\rho$ is
positive.  On-policy, $\rho=\mu$ and this is obviously true, for any
positive $B$. Thus, in the reversible case, nonlinear TD converges
on-policy, for any $B$.

@@

The first term $\transp{f}
\rho \Phi B\transp{\Phi}\rho f$ is always positive. For the second
term, since $A$ is antisymmetric, we have $\transp{x}Ax=0$ for all $x$.
Thus, we can add any multiple of $\transp{x}Ax=0$; let us take
$x=S^{-1}\rho f$:
\begin{equation}
\transp{f} \rho S^{-1}
A \Phi B\transp{\Phi}\rho f=
\transp{f} \rho S^{-1}A (S^{-1}-\Phi B\transp{\Phi})\rho f
\end{equation}

@@

Thus we have a two-timescale algorithm for non-linear TD in the off-policy
overparameterized case.

@@

>>>>

In the reversible case, $\mu\Delta$ is symmetric.\footnote{$\rho \Delta$
can be symmetric if and only if $\rho=\mu$. Indeed, if $\rho \Delta$ is
symmetric then $\rho=\rho'$ and $\rho$ is the stationary distribution.} We can use the
Dirichlet form which amounts to $L\deq\mu(\mu\Delta)^{-1}\mu$; then
$L\Delta=\mu$ and we have to prove that $\mu\Phi B\transp{\Phi}\rho$ is
positive.  On-policy, $\rho=\mu$ and this is obviously true, for any
positive $B$. Thus, in the reversible case, nonlinear TD converges
on-policy, for any $B$. It does so by minimizing the Dirichlet norm.

@@

The first term $\transp{f}
\rho \Phi B\transp{\Phi}\rho f$ is always positive. For the second
term, since $A$ is antisymmetric, we have $\transp{x}Ax=0$ for all $x$.
Thus, we can add any multiple of $\transp{x}Ax=0$; let us take
$x=S^{-1}\rho f$:
\begin{equation}
\transp{f} \rho S^{-1}
A \Phi B\transp{\Phi}\rho f=
\transp{f} \rho S^{-1}A (\Phi B\transp{\Phi}-S^{-1})\rho f
\end{equation}

@@

Thus we have a two-timescale algorithm for non-linear TD in the off-policy
overparameterized case; it minimizes the Dirichlet norm. TODO WRONG: $S$
is not necessarily positive!!!!! is positive if $\rho=\mu$.

TODO: Why do I end up using $\rho\Delta+\transp{(\rho \Delta)}$ while the
Dirichlet form is $\rho \Delta + \rho'-\transp{(\rho P)}$ which is
different, I think...

@@

Nonlinear GTD2 etc use a function $L$ that depends on $\theta$ (via
$\Phi$); this adds Hessian terms to the gradient of $L$, and it's not
obvious how to interpret the local minima of $L$.
